---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<!-- badges: start -->
[![R build status](https://github.com/tmsalab/edina/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/edina/actions)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
[![CRAN Version Badge](http://www.r-pkg.org/badges/version/edina)](https://cran.r-project.org/package=edina)
[![CRAN Status](https://cranchecks.info/badges/worst/edina)](https://cran.r-project.org/web/checks/check_results_edina.html)
[![RStudio CRAN Mirror's Monthly Downloads](http://cranlogs.r-pkg.org/badges/edina?color=brightgreen)](http://www.r-pkg.org/pkg/edina)
[![RStudio CRAN Mirror's Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/edina?color=brightgreen)](http://www.r-pkg.org/pkg/edina)
[![Coverage status](https://codecov.io/gh/tmsalab/edina/branch/master/graph/badge.svg)](https://codecov.io/github/tmsalab/edina?branch=master)
<!-- badges: end -->

# `edina` R package

Perform a bayesian estimation of the Exploratory 
Deterministic Input, Noisy "And" Gate (EDINA)
cognitive diagnostic model described by Chen et al. (2018)
<doi:10.1007/s11336-017-9579-4>.

## Installation

You can install `edina` from CRAN using:

```{r cran-installation, eval = FALSE}
install.packages("edina")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r gh-installation, eval = FALSE}
if(!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("tmsalab/edina")
```

## Usage

To use the `edina` package, load it into _R_ using:

```{r example, message = FALSE}
library("edina")
```

From there, the EDINA model can be estimated using:

```{r edina-est, eval = FALSE}
edina_model = edina(<data>, chain_length = 10000)
```

To compute a model underneath different _K_ attribute configured _Q_ matrices, use:

```{r edina-multiple, eval = FALSE}
edina_model = auto_edina(<data>, k = 2:4, chain_length = 10000)
```

**Note:** Higher _K_ configured _Q_ matrices take longer to estimate. 

## Authors

James Joseph Balamuta, Steven Andrew Culpepper, and Jeffrey A. Douglas

## Citing the `edina` package

To ensure future development of the package, please cite `edina`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("edina")
```

## License

GPL (>= 2)
