---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edina

<!-- badges: start -->
[![R-CMD-check](https://github.com/tmsalab/edina/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tmsalab/edina/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Perform a Bayesian estimation of the Exploratory 
Deterministic Input, Noisy "And" Gate (EDINA)
cognitive diagnostic model described by Chen et al. (2018).

## Installation

You can install `edina` from CRAN using:

```{r}
#| label: cran-installation
#| eval: false
install.packages("edina")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r}
#| label: gh-installation
#| eval: false
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("tmsalab/edina")
```

## Usage

To use the `edina` package, load it into _R_ using:

```{r}
#| label: edina-package
#| message: false
library("edina")
```

From there, the EDINA model can be estimated using:

```{r}
#| label: edina-est
#| eval: false
edina_model = edina(<data>, chain_length = 10000)
```

To compute a model underneath different _K_ attribute configured _Q_ matrices, use:

```{r}
#| label: edina-multiple
#| eval: false
edina_model = auto_edina(<data>, k = 2:4, chain_length = 10000)
```

**Note:** Higher _K_ configured _Q_ matrices take longer to estimate. 

## Authors

James Joseph Balamuta, Steven Andrew Culpepper, and Jeffrey A. Douglas

## Citing the `edina` package

To ensure future development of the package, please cite `edina`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r}
#| label: edina-citation
#| eval: false
citation("edina")
```

## License

GPL (>= 2)
